Self Regulation Ontology Retest Analyses

### 2018-08-09 code/SRO_Retest_Analyses.Rmd
added new intratrial analyses

'acc', 'avg_rt', 'conceptual_responses', 'fail_to_maintain_set',
       'learning_rate', 'learning_to_learn', 'nonperseverative_errors',
       'perseverative_errors', 'perseverative_responses', 'total_errors'

@@

# write.csv(trial_num_rel_df, paste0(retest_data_path, 'trial_num_rel_df_tbt.csv'))
```

@@

```{r warning=FALSE, message=FALSE}
trial_num_rel_df = read.csv(paste0(retest_data_path, 'trial_num_rel_df_tbt.csv'))

cols <- c("Accuracy" = '#084594', "Average RT error" = '#99000d', "SD RT error" = '#cb181d', "Average RT correct" = '#ef3b2c', "SD RT correct" = '#fb6a4a', "Missed percentage" = '#2171b5', "Cue switch cost RT (100)" = '#fc9272', "Cue switch cost RT (900)" = '#fcbba1', "Task switch cost RT (100)" = '#fee0d2', "Task switch cost RT (900)" = '#fff5f0', "Cue switch cost Acc (100)" = '#4292c6', "Cue switch cost Acc (900)" = '#6baed6', "Task switch cost Acc (100)" = '#9ecae1', "Task switch cost Acc (900)" = '#c6dbef')

cols <- c("Accuracy" = '#084594', "Average RT error" = '#99000d', "Average RT correct" = '#ef3b2c', "Missed percentage" = '#2171b5', "Cue switch cost RT (100)" = '#fc9272', "Cue switch cost RT (900)" = '#fcbba1', "Task switch cost RT (100)" = '#fee0d2', "Task switch cost RT (900)" = '#fff5f0', "Cue switch cost Acc (100)" = '#4292c6', "Cue switch cost Acc (900)" = '#6baed6', "Task switch cost Acc (100)" = '#9ecae1', "Task switch cost Acc (900)" = '#c6dbef')

trial_num_rel_df %>%
  gather(key, value, -breaks) %>%
  ggplot(aes(breaks, value, color=key))+
  geom_point()+
  geom_line()+
  theme_bw()+
  xlab("Number of trials")+
  ylab("ICC")+
  theme(legend.title = element_blank(),
        legend.position = 'bottom')+
  ylim(-1,1)

>>>>

@@

# write.csv(trial_num_rel_df, paste0(retest_data_path, 'trial_num_rel_df_shift.csv'))
```

@@

```{r warning=FALSE, message=FALSE}
trial_num_rel_df = read.csv(paste0(retest_data_path, 'trial_num_rel_df_shift.csv'))

trial_num_rel_df %>%
  gather(key, value, -breaks) %>%
  ggplot(aes((breaks+1)*10, value, shape=key))+
  geom_point()+
  geom_line(alpha = 0.5)+

  theme_bw()+
  xlab("Number of trials")+
  ylab("ICC")+
  theme(legend.title = element_blank(),
        legend.position = 'bottom')+
  scale_shape_manual(values = c(0:9),
                     breaks = c("acc_icc", "avg_rt_icc", "conceptual_responses_icc", "fail_to_maintain_set_icc", "learning_rate_icc", "learning_to_learn_icc", "nonperseverative_errors_icc", "perseverative_errors_icc", "perseverative_responses_icc", "total_errors_icc"),
                     labels = c("Accuracy", "Average Response Time", "Conceptual Responses", "Failure to Maintain Set", "Learning Rate", "Learning to Learn",  "Nonperseverative Errors", "Perseverative Errors", "Perseverative Responses", "Total Errors"))
